\documentclass{htresume}
\begin{document}

% HEADER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.4\textwidth}
\vspace{-\baselineskip}
\firstlastname{Henry To}
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\vspace{-\baselineskip}
\contactinfo{\phonenumber{555}{555}{5555}}{\emailaddress{hello@henry.to}}
\end{minipage}
\begin{minipage}[t]{0.35\textwidth}
\vspace{-\baselineskip}
\contactinfo{\website{linkedin.com/in/rakukojin}{Linkedin}}{\website{github.com/henrito}{Github}}
\end{minipage}
\vspace{6pt}

% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\coloredsection{Education}
\degreeitemize{\href{https://uci.edu}{University of California Irvine}}{
  \degreeitem{2017}{B.S. Computer Science}{awarded with a specialization in Architecture and Embedded Systems}
  \degreeitem{2011}{B.A. Japanese Language and Literature}{}
}

% WORK EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\coloredsection{Work Experience}
\freelancingexperience{2017}{Present}{{Freelance Developer}\dotdivider{Freelance QA Tester}}
\begin{itemize}[noitemsep]
  \item Designed and implemented Shopify/Squarespace UI/UX to better showcase clients' products.
  \item Ensured game titles complied with Sony's TRC and Microsoft's TCR certification standards.
\end{itemize}
\workexperience{2012}{2016}{QA Project Lead}{\href{http://digitalheartsusa.com}{DIGITAL Hearts USA Inc.}}
\begin{itemize}[noitemsep]
  \item Tested dozens of successfully shipped titles from clients such as Namco, Square-Enix, Capcom, Atlus, etc.
  \item Coordinated multiple teams of testers and trained senior testers to become successful project leads.
  \item Developed and maintained reusable test plans and documentation to efficiently meet clients' requirements.
\end{itemize}
\workexperience{2013}{2014}{Mobile QA Tester}{\href{https://nexonm.com}{Nexon M Inc.}}
\begin{itemize}[noitemsep]
  \item Provided essential feedback early in development, leading to significant improvements to overall gameplay.
  \item Assisted in the creation of test plans to be used on all future Nexon M game titles.
\end{itemize}

% SKILLS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.5\textwidth}
\coloredsection{Proficient Languages}
\skillitemize{5em}{
  \skillitem{Proficient}{{C}\dotdivider{C++}}
}
\coloredsection{Familiar Languages}
\skillitemize{4.5em}{
  \skillitem{Coding}{{Java}\dotdivider{VHDL}}
  \skillitem{Scripting}{{Python}\dotdivider{Ruby}\dotdivider{JavaScript}}
  \skillitem{Markup}{{HTML}\dotdivider{CSS}\dotdivider{LaTeX}}
  \skillitem{Shader}{GLSL}
}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\coloredsection{Non-Technical Skills}
\skillitemize{5.5em}{
  \skillitem{Languages}{{English}\dotdivider{Chinese (Teochew)}\dotdivider{Japanese}}
}
\coloredsection{Technical Skills}
\skillitemize{8em}{
  \skillitem{Frameworks}{{Cocoa}\dotdivider{Win32}\dotdivider{Xlib}\dotdivider{OpenGL}}
  \skillitem{Microcontrollers}{{AVR}\dotdivider{ESP8266}\dotdivider{MSP430}}
  \skillitem{Tools}{{JIRA}\dotdivider{Git}\dotdivider{GCC}\dotdivider{LLVM}\dotdivider{Valgrind}}
}
\end{minipage}

% PROJECTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\coloredsection{Projects}
\projectitemize{
  \projectitem{OpenGL windowing library}{Manages the creation/destruction of OpenGL Windows on macOS, Windows and Linux.}
  \projectitem{SSD1531 graphics library}{Supports tile-based sprites and scrolling backgrounds using an ESP8266.}
  \projectitem{Predefined C macro library}{Identifies architectures, compilers, platforms and standards at compile time.}
  \projectitem{IFF/ILBM parser library}{Supports parsing/reading/writing/compression/decompression of IFF/ILBM chunks.}
  \projectitem{WS8211 LED rave totem}{Controls WS8211 LED strips with an ATTiny85 to display various animations.}
  \projectitem{Obstacle avoidance robot}{Arduino-based 4-wheeled robot utilizing an HC-SR04 sensor to avoid obstacles.}
  \projectitem{MIPS processor in VHDL}{Implementation of a processor that can execute a subset of MIPS ISA.}
}

\end{document}
